---
title: "PREDICTION OF LIKELIHOOD OF CREDITCARD APPROVAL"
author: "ANU PAHALJANI"

---

Please read all instructions carefully.  Fill in all fields above (Espicially your student number). To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with chinese characters.
Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevent output.


**DESCRIPTIVE ANALYSIS OF CREDIT CARD DATA**
**PART1**

```{r Load the data}
  #load the data

setwd("C:/Users/Anu/Desktop/MKT436R/HW3")
creditcardData <- read.csv("ccard.csv")
creditcardData_no_exp = creditcardData
creditcardData_no_exp$expenditure = NULL
#end
```


**Using MARS using earth function & Plotmo for realtionships**
```{r Question 1B}

#install.packages('earth', repos='http://cran.us.r-project.org')
library('earth')
earthFit = earth(card~.,data=creditcardData, degree=2)
plotmo(earthFit)


#end
```

**COMMENTS ON THE ABOVE ANALYSIS**

The probability of approval increases as your spend more on your card, at the same time expenses should be in proprotion to the income,indicated by share.As share increases the propability of approval decreases sharply. When you have more than a certain amount on active cards, it depends on how much you spend on those cards.


**PREDICTIVE MODEL: PREDICT WHETHER AN APPLICANT WOULD BE APPROVED FOR CREDIT CARD**
**PART2a: Expenditure of the consumer not considered in this Model**
```{r Question 2A}


library('earth')
creditcardData <- read.csv("ccard.csv")
creditcardData_no_exp = creditcardData
creditcardData_no_exp$expenditure = NULL
data("creditcardData_no_exp")

#10-fold Cross Validation
set.seed(1) 
nFold = 10
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(creditcardData_no_exp))*nFold)+1

getDetailRMSE = function(modelCall){
	modelPerformance = rep(NA,nFold)
	for(fold in 1:nFold){
		#Step 2i: Get the training and validation data for this fold
		trainingData = subset(creditcardData_no_exp,valNum!=fold)
		validationData = subset(creditcardData_no_exp,valNum==fold)
		
		#Step 2ii: Estimate the models for this training data
		model = update(modelCall,data=trainingData)
		#Step 2iii: Calculate out of sample MSE for this validationData
		validRMSE =  mean((validationData$card - predict(model,validationData))^2)^.5
		#Store model performance		
		modelPerformance[fold] = validRMSE
	}
  return(mean(modelPerformance))
}

#Different Models considered for Regression: LINEAR MODEL
lm1= lm(card~.,data=creditcardData_no_exp)#for full set of interaction
lm2=lm(card~. ^2,data=creditcardData_no_exp)
lm3= lm(card~.^2,data=creditcardData_no_exp[,-c(3,7,9)])
lm4=lm(card~reports+income+share+owner+majorcards+active+reports*share+reports*owner+ reports*majorcards+income*dependents,data=creditcardData)
getDetailRMSE(lm4)
anova(lm4)

      
#Different Models considered for Regression: NON-LINEAR -MARS MODEL
earth1= earth(card~.,data=creditcardData_no_exp)#for full set of interaction
earth2=earth(card~.,data=creditcardData_no_exp, degree=2)
earth3=earth(card~.,data=creditcardData_no_exp,thres=0)
earth4=earth(card~.,data=creditcardData_no_exp,thres=0.01)
earth5=earth(card~.,data=creditcardData_no_exp,thres=0.1)
earth6=earth(card~reports+income+share+owner+majorcards+active+reports*share+reports*owner+ reports*majorcards+income*dependents, data=creditcardData)

#MODEL CHOSEN WITH THE LOWEST RMSE
chosenModel1=earth1

```



**PART2b: Expenditure of the consumer is considered in this Model**
```{r Question 2B}

library('earth')
creditcardData <- read.csv("ccard.csv")
data("creditcardData")

#10-fold Cross Validation

set.seed(1) 
nFold = 10
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(creditcardData))*nFold)+1

getDetailRMSE = function(modelCall){
	modelPerformance = rep(NA,nFold)
	for(fold in 1:nFold){
		#Step 2i: Get the training and validation data for this fold
		trainingData = subset(creditcardData,valNum!=fold)
		validationData = subset(creditcardData,valNum==fold)
		
		#Step 2ii: Estimate the models for this training data
		model = update(modelCall,data=trainingData)
		#Step 2iii: Calculate out of sample MSE for this validationData
		validRMSE =  mean((validationData$card - predict(model,validationData))^2)^.5
		#Store model performance		
		modelPerformance[fold] = validRMSE
	}
  return(mean(modelPerformance))
}




#Different Models considered for Regression: LINEAR MODEL
lm6= lm(card~.,data=creditcardData)#for full set of interaction
lm7=lm(card~. ^2,data=creditcardData)
lm8= lm(card~. +reports*share+reports*expenditure+income*share+share*expenditure+expenditure*active, data=creditcardData)
lm9=lm(card~.^2,data=creditcardData[,-c(3,8,10)])
lm10=lm(card~reports+income+share+expenditure+owner+dependents+majorcards+active+reports*share+reports*expenditure+reports*share+ income*share+income*expenditure+income*dependents+share*expenditure+share*owner+expenditure*majorcards+expenditure*active+owner*majorcards,data=creditcardData)

        



#Different Models considered for Regression: NON-LINEAR -MARS MODEL

earth6= earth(card~.,data=creditcardData)#for full set of interaction
earth7=earth(card~.,data=creditcardData, degree=2)
earth8= earth(card~.,data=creditcardData[,-c(3,8,10)])
earth9=earth(card~.,data=creditcardData,thres=0)
earth10=earth(card~.,data=creditcardData,thres=0.01)
earth11=earth(card~.,data=creditcardData,thres=0.1)

#MODEL CHOSEN WITH THE LOWEST RMSE
chosenModel2=(earth6)

```

```{r}
 save(chosenModel1, chosenModel2, file = '31427166.Rdata')

```