---
title: "ASHOK PAHALAJANI, ANURADHA, 31427166 - Homework 3"
author: "ASHOK PAHALAJANI, ANURADHA, 31427166"
output: html_document
---

Please read all instructions carefully.  Fill in all fields above (Espicially your student number). To allow this file to be knit, you might need to save it in a new location, as you do not have write permissions in the dropbox folder, and R does not work well with chinese characters.
Do not comment out the lines that produce output.  Check your html file before submission to ensure it has all relevent output.



**Question 1A:**
```{r Question 1A}
#Load the data   

setwd("C:/Users/Anu/Desktop/MKT436R/HW3")
creditcardData <- read.csv("Student Data 6.csv")
creditcardData_no_exp = creditcardData
creditcardData_no_exp$expenditure = NULL
#end
```


**Question 1B:**
```{r Question 1B}
#Using MARS using earth function & Plotmo for realtionships

#install.packages('earth', repos='http://cran.us.r-project.org')
library('earth')
earthFit = earth(card~.,data=creditcardData, degree=2)
plotmo(earthFit)


#end
```

**Question 1C:**

The probability of approval increases as your spend more on your card, at the same time expenses should be in proprotion to the income,indicated by share.As share increases the propability of approval decreases sharply. When you have more than a certain amount on active cards, it depends on how much you spend on those cards.


**Question 2A:**
```{r Question 2A}

library('earth')
creditcardData <- read.csv("Student Data 6.csv")
creditcardData_no_exp = creditcardData
creditcardData_no_exp$expenditure = NULL
data("creditcardData_no_exp")


set.seed(1) 
nFold = 10
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(creditcardData_no_exp))*nFold)+1

getDetailRMSE = function(modelCall){
	modelPerformance = rep(NA,nFold)
	for(fold in 1:nFold){
		#Step 2i: Get the training and validation data for this fold
		trainingData = subset(creditcardData_no_exp,valNum!=fold)
		validationData = subset(creditcardData_no_exp,valNum==fold)
		
		#Step 2ii: Estimate the models for this training data
		model = update(modelCall,data=trainingData)
		#Step 2iii: Calculate out of sample MSE for this validationData
		validRMSE =  mean((validationData$card - predict(model,validationData))^2)^.5
		#Store model performance		
		modelPerformance[fold] = validRMSE
	}
  return(mean(modelPerformance))
}

#LINEAR MODEL
lm1= lm(card~.,data=creditcardData_no_exp)#for full set of interaction
lm2=lm(card~. ^2,data=creditcardData_no_exp)
lm3= lm(card~.^2,data=creditcardData_no_exp[,-c(3,7,9)])
lm4=lm(card~reports+income+share+owner+majorcards+active+reports*share+reports*owner+ reports*majorcards+income*dependents,data=creditcardData)
getDetailRMSE(lm4)
anova(lm4)

      
#MARS MODEL
earth1= earth(card~.,data=creditcardData_no_exp)#for full set of interaction
earth2=earth(card~.,data=creditcardData_no_exp, degree=2)
earth3=earth(card~.,data=creditcardData_no_exp,thres=0)
earth4=earth(card~.,data=creditcardData_no_exp,thres=0.01)
earth5=earth(card~.,data=creditcardData_no_exp,thres=0.1)
earth6=earth(card~reports+income+share+owner+majorcards+active+reports*share+reports*owner+ reports*majorcards+income*dependents, data=creditcardData)

chosenModel1=earth1

```



**Question 2B:**
```{r Question 2B}

library('earth')
creditcardData <- read.csv("Student Data 6.csv")
data("creditcardData")


set.seed(1) 
nFold = 10
#Step 1: Randomly choose which fold each row is in 
valNum = floor(runif(nrow(creditcardData))*nFold)+1

getDetailRMSE = function(modelCall){
	modelPerformance = rep(NA,nFold)
	for(fold in 1:nFold){
		#Step 2i: Get the training and validation data for this fold
		trainingData = subset(creditcardData,valNum!=fold)
		validationData = subset(creditcardData,valNum==fold)
		
		#Step 2ii: Estimate the models for this training data
		model = update(modelCall,data=trainingData)
		#Step 2iii: Calculate out of sample MSE for this validationData
		validRMSE =  mean((validationData$card - predict(model,validationData))^2)^.5
		#Store model performance		
		modelPerformance[fold] = validRMSE
	}
  return(mean(modelPerformance))
}




#LINEAR MODEL
lm6= lm(card~.,data=creditcardData)#for full set of interaction
lm7=lm(card~. ^2,data=creditcardData)
lm8= lm(card~. +reports*share+reports*expenditure+income*share+share*expenditure+expenditure*active, data=creditcardData)
lm9=lm(card~.^2,data=creditcardData[,-c(3,8,10)])
lm10=lm(card~reports+income+share+expenditure+owner+dependents+majorcards+active+reports*share+reports*expenditure+reports*share+ income*share+income*expenditure+income*dependents+share*expenditure+share*owner+expenditure*majorcards+expenditure*active+owner*majorcards,data=creditcardData)

        



#MARS MODEL

earth6= earth(card~.,data=creditcardData)#for full set of interaction
earth7=earth(card~.,data=creditcardData, degree=2)
earth8= earth(card~.,data=creditcardData[,-c(3,8,10)])
earth9=earth(card~.,data=creditcardData,thres=0)
earth10=earth(card~.,data=creditcardData,thres=0.01)
earth11=earth(card~.,data=creditcardData,thres=0.1)

chosenModel2=(earth6)

```

```{r}
 save(chosenModel1, chosenModel2, file = '31427166.Rdata')

```